---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# compliment

<!-- badges: start -->
<!-- badges: end -->

compliment generates randomized, uplifting compliments and farewells by
combining adjectives, traits, and closings from built-in word banks.

## Installation

You can install the development version of compliment from
[GitHub](https://github.com/guadapascal/compliment) with:

``` r
# install.packages("pak")
pak::pak("guadapascal/compliment")
```

## Usage

Generate a single compliment:

```{r example}
library(compliment)

compliment()
```

Generate several compliments at once with `n`:

```{r}
compliment(5)
```

`compliment()` validates its input, so non-numeric or non-positive values
of `n` raise an informative error:

```{r, error = TRUE}
compliment(0)
```

Generate a random goodbye with `farewell()`:

```{r}
farewell()
```

Like `compliment()`, it also accepts `n` to generate several at once:

```{r}
farewell(3)
```
